---
title: "pset_4"
author: "Andrea Lamas-Nino"
date: "2/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse )
library(devtools)
library(readr)
library(ggplot2)
library(tidyr)
library(glue)
library(gt)

## Load data.
elections <- read_csv("ps_4_elections-poll-nc09-3.csv") %>% 
  filter(response%in%c("Dem","Rep","Und"), educ4!="[DO NOT READ] Refused",gender!= "[DO NOT READ] Refused", race_eth!="[DO NOT READ] Refused", file_race_black!="[DO NOT READ] Refused")
```

## Problem 1

```{r one, echo=FALSE}
## There were x respondents who supported the Dem candidate.

dem_support <- elections %>% 
  filter(response=="Dem") %>% 
  tally()

# Other method:
# elections %>% 
#   group_by(response) %>% 
#   summarize(support_count=n()) %>% 
#   filter(response=="Dem") %>% 
#   select(support_count)

## There were X more respondents who favored the Republican candidate than who were Undecided.

rep_support<- elections %>% 
  filter(response=="Dem") %>% 
  tally()

und_support<- elections %>% 
  filter(response=="Und") %>% 
  tally()

rep_support-und_support

## There are two gender variables (gender and gender_combined). There are X individuals for whom these variables have different values.
gender_combined_count <- elections %>% 
  group_by(gender_combined) %>% 
  summarize(count=n())
gender_count<- elections %>% 
  group_by(gender) %>% 
  summarize(count=n())
gender_difference <- gender_combined_count$count-gender_count$count
gender_difference[1]

## There are X respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.
white_count_re <- elections %>% 
  filter(race_eth=="White") %>% 
  summarize(count=n())
white_count_frb<- elections %>% 
  filter(file_race_black=="White") %>% 
  summarize(count=n())
white_difference <- white_count_frb$count-white_count_re$count
white_difference[1]

## The first response of Rep came X minutes (rounded to the nearest minute) before the first response of Dem.
first_rep_response<-elections %>% 
  filter(response=="Rep") %>% 
  summarize(first_rep_response=min(timestamp))
first_dem_response<-elections %>% 
  filter(response=="Dem") %>% 
  summarize(first_dem_response=min(timestamp))
first_rep_response-first_dem_response

```
There were `r dem_support` respondents who supported the Dem. candidate.

There were `r rep_support-und_support` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (gender and gender_combined). There are `r gender_difference[1]` individuals for whom these variables have different values.

There are `r white_difference[1]` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Rep came `r first_rep_response-first_dem_response` minutes (rounded to the nearest minute) before the first response of Dem.
## Including Plots


```{r pressure, echo=FALSE}
 elections %>% 
   select(response, race_eth, final_weight) %>% 
   group_by(race_eth, response) %>% 
   
   summarize(total = sum(final_weight)) %>%   
   filter(race_eth != "[DO NOT READ] Don't know/Refused") %>% 
   spread(key =  response, value = total) %>% 
   mutate(all = Dem + Rep + Und) %>% 
   mutate(Dem = Dem / all) %>% 
   mutate(Rep = Rep / all) %>% 
   mutate(Und = Und / all) %>% 
   select(-all) %>% 
  
   
   ungroup() %>% 
   
   gt() %>% 
   tab_header(
     title = "Polling Results in North Carolina 9th Congressional District") %>% 
   
   cols_label(
     race_eth = "Race",
     Dem = "DEM.",
     Rep = "REP.",
     Und = "UND."
   ) %>%
   
   fmt_percent(columns = vars(Dem, Rep, Und),
               decimals = 0) 

# Worked with the code Preceptor put on Piazza.
```

## Collaboration: Worked with the code Preceptor put on Piazza.
